---
title: "ArcDiagram"
author: "Iain  Emsley"
date: "2023-06-28"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

An effort to use an arc diagram to show the relative links between the Mastodon social code of conduct. 

```{r cars}
library('stringdist')
library('ggplot2')
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
codes_df = read.csv("~/Desktop/noracism.csv")
colnames(codes_df) <- c("site", "id", "code")
codes_df
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plo
```{r base, eval=FALSE}
base_str = "No racism, sexism, homophobia, transphobia, xenophobia, or casteism"
```
Now that we have hteh ebase string. 
Let's count the levenshtein differences
```{r calc_distance, eval=FALSE}
codes_df$dist = unlist(lapply(codes_df$code, function(x) { stringdist(base_str, x, method = "lv") }))
codes_df
```
Let's add the time here
```{r prepData, eval=FALSE}
instances_df = read.csv("~/Desktop/blocked_db.csv")

arc_df = merge(codes_df, instances_df, by.x="site", by.y="name")
arc_df$dtime = as.Date(unlist(lapply(arc_df$added, function(w) { as.Date(w)} )) ,  format = "%d-%m-%Y" )
#arc_df$odtime = as.Date(unlist(lapply(arc_df$added, function(w) { as.Date("2012-11-21")} )),  format = "%Y-%m-%d" )
arc_df
#write.csv(arc_df, "~/Desktop/levenshtein.csv")
```
Graph as timeline with arcs
```{r graph}
#set plot sixe

q = ggplot(arc_df) +
  scale_x_date(breaks =seq(as.Date("01-09-2016", format = "%d-%m-%Y"), 
                           max(as.Date(arc_df$dtime, format = "%d-%m-%Y")), by="6 months"), 
               date_labels = "%b %Y" ) + 
  xlab("Date") +
  ylab("Levenshtein Edit Distance") +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
  ylim(0, 0.1)
for (i in 1:nrow(arc_df)) {
  if (arc_df[i, 'dtime'] != "1999-01-01") {
  q = q + geom_curve(aes(x = as.Date("01-09-2016",  format = "%d-%m-%Y"), y = 0, xend = dtime, yend =0, colour=dist), data = arc_df[i, ], curvature = -(arc_df[i, 'dist'])/100 )
  }
}

q 
ggsave("~/Desktop/edit.png", width = 30, height = 20, units = "cm")

```
Scatter plot of names and distances
```{r scatter}
arcs_df = arc_df[arc_df$dtime > as.Date("2016-01-01"), ]
ggplot(arcs_df, aes(x=dtime, y=dist)) +
  #geom_point() +
  geom_text(aes(x=dtime, y=dist, label=site)) +
  scale_x_date(breaks =seq(as.Date("01-01-2016", format = "%d-%m-%Y"), 
                           max(as.Date(arcs_df$dtime, format = "%d-%m-%Y")), by="1 month"), 
               date_labels = "%b %Y" ) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1),
        #axis.text.y=element_blank(),  #remove y axis labels
        #axis.ticks.y=element_blank()  #remove y axis ticks
        ) +
  xlab("Date") +
  ylab("Levenshtein Edit Distance")

ggsave("~/Desktop/scatter.png", width = 30, height = 20, units = "cm")
```
